---
title: "DevelopingDataProducts_CourseProject1"
author: "Angela"
date: "5/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, echo = FALSE, include = FALSE}
setwd("~/Documents/ContinuedLearning/Coursera_DataScience/Course9_DevelopingDataProducts")
library(leaflet)
library(tidyverse)
```

Import latitude and longitude of Florida cities from:   https://www.mapsofworld.com/usa/states/florida/lat-long.html   
Data taken from website on 4/28/2020 at 1:04 PM EST  

```{r import data 1, echo = FALSE, include = FALSE}
FLLatLng <- read.csv("~/Documents/ContinuedLearning/Coursera_DataScience/Course9_DevelopingDataProducts/Week2/FLLatLng.csv")

#Relabel the columns so they are consistent across data frames
colnames(FLLatLng)[1:3] <- c("City", "latitude", "longitude")

#Get rid of columns you will not use
FLLatLng <- FLLatLng[1:3]

#Clean up data so City column matches other dataframes
FLLatLng$City <- gsub(" city","", FLLatLng$City) #get rid of city
FLLatLng$City <- gsub(" town","", FLLatLng$City) #get rid of town
FLLatLng$City <- gsub(" ","", FLLatLng$City) #get rid of extra spaces at end of names
#Unfortunately this last piece of code also gets rid of space in between names of cities, we will have to alter the other data frames to match this
```

Import population of Florida cities from:  
https://www.florida-demographics.com/cities_by_population  
Data taken from website on 4/28/2020 at 1:07 PM EST  
Data from this website was extracted from the following sources:  

- United States Census Bureau. Annual Estimates of the Resident Population: April 1, 2010 to July 1, 2018. U.S. Census Bureau, Population Division. Web. May 2019. http://www.census.gov/.  
- United States Census Bureau. B01001 SEX BY AGE, 2018 American Community Survey 5-Year Estimates. U.S. Census Bureau, American Community Survey Office. Web. 19 December 2019. http://www.census.gov/.  

```{r import data 2, echo = FALSE, include = FALSE}
FLpopulation <- read.csv("~/Documents/ContinuedLearning/Coursera_DataScience/Course9_DevelopingDataProducts/Week2/FLpopulation.csv")

#Get rid of any ranking with the word TIE and convert to numeric
FLpopulation$Rank <- as.numeric(gsub("TIE","", FLpopulation$Rank))
FLpopulation$Rank <- as.numeric(as.character(FLpopulation$Rank))

#Convert population data to numeric (first get rid of commas)
FLpopulation$Population <- as.numeric(gsub(",","",FLpopulation$Population))
FLpopulation$Population <- as.numeric(as.character(FLpopulation$Population))

#Get rid of all spaces in City name to match the first data frame
FLpopulation$City <- gsub(" ","", FLpopulation$City)
```

Import each city/county from:  
https://dos.myflorida.com/library-archives/research/florida-information/government/local-resources/citycounty-list/  
Data taken from website on 4/28/2020 at 1:11 PM EST  

```{r import data 3, echo = FALSE, include = FALSE}
FLcitycounty <- read.csv("~/Documents/ContinuedLearning/Coursera_DataScience/Course9_DevelopingDataProducts/Week2/FLcitycounty.csv")

#Change column names
colnames(FLcitycounty)[1:3] <- c("County", "City", "Desc")

#Get rid of garbage columns
FLcitycounty <- FLcitycounty[1:3]

#Get rid of spaces in City name to match above data frames
FLcitycounty$City <- gsub(" ","", FLcitycounty$City)
```

Import stadiums in Florida from:  
https://en.wikipedia.org/wiki/Sports_teams_in_Florida  

```{r import data 4, echo = FALSE, include = FALSE}
StadiumsinFL <- read.csv("~/Documents/ContinuedLearning/Coursera_DataScience/Course9_DevelopingDataProducts/Week2/StadiumsinFL.csv")

#The symbol column contains links to the logos but we'll need to convert this into the proper code for leaflet to read

NHL <- makeIcon(
    iconUrl = "https://www-league.nhlstatic.com/images/logos/league-dark/133-flat.svg",
    iconWidth = 31*215/230,
    iconHeight = 31, 
    iconAnchorY = 16,
    iconAnchorX = 31*215/230/2)
MLB <- makeIcon(
    iconUrl = "https://www.mlbstatic.com/team-logos/league-on-dark/1.svg",
    iconWidth = 31*215/230,
    iconHeight = 31, 
    iconAnchorY = 16,
    iconAnchorX = 31*215/230/2)
MLS <-makeIcon(
    iconUrl = "https://league-mp7static.mlsdigital.net/styles/non-retina_desktop_logo/s3/logo25-77x77_0.png?LzMdhn2DU4GXKEjKfJ2QYWMaQKQIk7VQ&itok=ZtYZ58tI",
    iconWidth = 31*215/230,
    iconHeight = 31, 
    iconAnchorY = 16,
    iconAnchorX = 31*215/230/2)
NBA <-makeIcon(
    iconUrl = "https://seeklogo.net/wp-content/uploads/2014/09/NBA-logo.png",
    iconWidth = 31*215/230,
    iconHeight = 31, 
    iconAnchorY = 16,
    iconAnchorX = 31*215/230/2)
NFL <-makeIcon(
    iconUrl = "https://static.nfl.com/static/content/public/static/wildcat/assets/img/application-shell/shield/default.svg",
    iconWidth = 31*215/230,
    iconHeight = 31, 
    iconAnchorY = 16,
    iconAnchorX = 31*215/230/2)

myIconList2 <- iconList(NHL= NHL,
                    MLB = MLB, 
                    MLS = MLS,
                    NBA = NBA,
                    NFL = NFL)
myIconList <- iconList(MLB, NHL, NFL, NBA, MLS, MLB, NBA, NFL, NFL, MLS, NHL)
class(myIconList) <- "leaflet_icon_set"
```

Combine all dataframes into one

```{r combine datasets, echo = FALSE, include = FALSE}
#Want all city columns to be character so you can combine datasets easily 
FLLatLng$City <- as.character(FLLatLng$City)
FLpopulation$City <- as.character(FLpopulation$City)
FLcitycounty$City <- as.character(FLcitycounty$City)

#begin combining data frames and get rid of NA values
FLdata <- FLLatLng %>% 
    left_join(FLpopulation, by = "City") %>%
    left_join(FLcitycounty, by = "City") 
FLdata <- filter(FLdata, !is.na(FLdata$Rank))
FLdata <- filter(FLdata, !is.na(FLdata$County))
FLdata_test <- FLdata[2:3]
```

##Map of all Florida cities and major sports teams

```{r map 2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
FLdata <- arrange(FLdata, desc(Population))

FLdata_popup <- paste(FLdata$City, FLdata$Population, sep=": Population is ")

FLdata %>%
    leaflet() %>%
    addTiles() %>%
    addCircles(weight = 1, radius = sqrt(FLdata$Population)*40, popup = FLdata_popup) %>%
    addMarkers(lat = StadiumsinFL$Latitude, lng = StadiumsinFL$Longitude, icon = myIconList2[StadiumsinFL$League])
```


